Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2015-09-10 Documents/Paper/ms.tex
Removed duplicate figure
updated numbers

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{trace_logl.pdf}
\caption{\it A ``trace plot'' of the log likelihood in the sinusoidal model, for an
MCMC chain designed to sample the posterior distribution. The two phases
have log-likelihoods around -730 and -745 respectively, however transitions
between the two phases are quite uncommon.
\label{fig:trace_logl}}
\end{center}
\end{figure}

@@

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -771.8$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 39.8 nats.

>>>>

@@

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -772.7$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 41.4 nats.
